%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Frontend developper} % Job title
    {Oui.sncf} % Organization
    {La Défence, France} % Location
    {Octobre. 2018 - Septembre. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migration from  Angular 1.6 to React with test jest/enzyme}
        \item {Developpement of new feature and fixes  bug (web app and mails).}
        \item {Pock realised to teach to the team new syntax in react (hooks).}
        \item {Small presentation on rust the new system programming language and it concepts (ownership and borrowing).}
      \end{cvitems}
    }
%---------------------------------------------------------
\cventry
  {Backend developper} % Job title
  {Club Med} % Organization
  {Paris, France} % Location
  {Mai. 2018 - Sept. 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Conception and estimation of users stories.}
      \item {New feature and bug fixes.}
    \end{cvitems}
  }

%---------------------------------------------------------
%---------------------------------------------------------
  \cventry
    {FrontEnd developper} % Job title
    {Canal plus} % Organization
    {Issy-les-moulineaux, France} % Location
    {Avril. 2017 - Avril. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conception and estimation of users stories.}
        \item {New feature and bug fixes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {FullStack developper} % Job title
    {MyNewMood} % Organization
    {Issy-les-moulineaux, France} % Location
    {Sept. 2016 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Conception and implementation of mobile app  with Angular2/typescript.}
        \item {Handling of state and events with Ngrx2.}
        \item {Developpement of mobile map with google map api.}
        \item {Automated the AWS lambda workflow developpement with serverless libs}
        \item {Developpement of AWS lamdda Node.Js function}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {FrontEnd developper} % Job title
    {Kpler} % Organization
    {Paris, France} % Location
    {Jan. 2016 - Juil. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implementation of many crtical features for  data-scientists.}
        \item {Added svg Elements on map}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Developper} % Job title
    {STI} % Organization
    {Evry, France} % Location
    {Juil. 2011 - Avril. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develoeppement of multi-platform app in Qt/C++.}
        \item {Integration of an embededd SQLITE database to store and process more easily data}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
